---
title: "Avocado"
author: "Aman Kashyap"
date: "11/5/2021"
output:
  html_document: default
---

## setting up environment
notes: Setting up environment by loading "tidyverse","ggplot2" and "dplyr" packages

```{r loading packages}
library(tidyverse)
library(dplyr)
library(ggplot2)
```
##first we upload the Dataset of avocado

```{r}
avocado <- read.csv("D:\\data_analyst\\SQL practice\\avocado.csv")
head(avocado)
```
### Now we create our First dataFrame 
notes: In which we find Average sales of Small.Bags,large.Bags,Xlarge.Bags and Total.Bags
```{r}
Average_bags<-avocado %>% 
 group_by(region,year) %>% 
  summarise(Average_small_bags=mean(Small.Bags),
            Average_large_bags=mean(Large.Bags),
            Average_XLarge_bags=mean(XLarge.Bags),
            Total_bags=mean(Total.Bags))

head(Average_bags)
```
### After this we create a Dataframe which have Average Total bags Above 10Lakh
```{r}
Total_bags_df<-Average_bags %>% 
  filter(Total_bags>1000000)

head(Total_bags_df)
```
### Here is the Grape Visual of DataFrame 
Average Total Bags Above 10Lakh

```{r}
ggplot(data = Total_bags_df)+
  geom_point(mapping = aes(x=Total_bags,y=year,color=region))+
  labs(title = "Average Total Bags Above 1000000")
```
##Now we create our another Dataframe of Average Total bags below 10000

```{r}
Total_bags_df1<-Average_bags %>% 
  filter(Total_bags<10000)

head(Total_bags_df1)
```
### Here is the Grape visual of Dataframe 
Average Total Bags below 10000 

```{r}
ggplot(data = Total_bags_df1)+
  geom_point(mapping = aes(x=Total_bags,y=year,color=region))+
  labs(title = "Average Total Bags under 10000")
```

